FinalManuscript_DISCS_UG

### 2018-09-23 parts/01_introduction_05scopeandlimitations.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme developed by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis
        \begin{enumerate}
            \item Number of Pixel Change Rate (NPCR)
            \item Universal Average Change Intensity (UACI)
        \end{enumerate}
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis
        \begin{enumerate}
            \item Number of Pixel Change Rate (NPCR)
            \item Universal Average Change Intensity (UACI)
        \end{enumerate}
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

### 2018-09-23 parts/08_appendices_a_cryptosystems.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.

\section{Description of basic cryptosystems used}
\subsection{Pallier cryptosystem}
\subsection{Key generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm\lcm(p-1,q-1)$.

Define the public key as $(g,n)$ and the private key
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2}
\end{align*}
\subsection{Homomorphic properties}
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a constant)}\\
    D(E(m_1)^{m_2}\bmod n^2)= m_1m_2\bmod n & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}

>>>>

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{DESCRIPTION OF CRYPTOSYSTEMS}
\section{Pallier cryptosystem}
\subsection{Key generation}
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.

Define the public key as $(g,n)$ and the private key
\begin{align*}
  E(m) = g^m \cdot r^n \mod{n^2}
\end{align*}
\subsection{Homomorphic properties}
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a constant)}\\
    D(E(m_1)^{m_2}\bmod n^2)= m_1m_2\bmod n & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}
\section{Performing real number operations using integer-based cryptosystems}

### 2018-09-23 parts/08_appendices_b_numericalapproximations.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

%\begin{enumerate}
%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
%\item The sequence of front matter must be as follows:
%    \begin{enumerate}
%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
%    \item Abstract
%	\item Table of Contents
%	\item List of Figures
%	\item List of Tables
%	\end{enumerate}
%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
%\end{enumerate}
\section{Numerical approximations}
In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
\subsection{Approximation for $\log(1+x)$}

We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{(1+\frac{1}{n})}.
\end{align*}
This integral can be approximated using Legendre-Gauss quadrature.

\subsection{Approximation for $x^r$}
To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
\end{align*}
This expression can then be approximated using the Taylor series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.

>>>>

%\begin{enumerate}
%\item There should be NO PAGE NUMBERS on the first page of every chapter/section..
%\item Tables must have NO VERTICAL LINES, as well as NO INNER HORIZONTAL LINES after the table headers.
%\item Figures and tables are numbered ACCORDING TO CHAPTER NUMBER (e.g. Table 3.1 must be located in Chapter 3, and Figure B.2 is in Appendix B).
%\item The sequence of front matter must be as follows:
%    \begin{enumerate}
%    \item Title Page, in the correct formatting (e.g. Titles must be written in an inverted triangle, in ALL CAPS and boldface)
%    \item Abstract
%	\item Table of Contents
%	\item List of Figures
%	\item List of Tables
%	\end{enumerate}
%\item Upon binding, the front cover must contain the EXACT CONTENT AND FORMAT as that of your thesis’ title page.
%\end{enumerate}
\chapter{NUMERICAL APPROXIMATIONS}
In order to calculate a function under a additively and multiplicatively homomorphic cryptosystem, it is necessary to express the function in terms of addition and multiplication operations.
In this section, we discuss approximation for the logarithm ($\log(1+x)$) and power ($x^\gamma$) functions using only addition, subtraction, multiplication, and division operations.
%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
%TODO: Include citations for this chapter
\section{Approximation for $\log(1+x)$}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align*}
This integral can be approximated using the five-point Gauss-Legendre quadrature rule, yielding the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) =
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.6\linewidth,\keepaspectratio]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}
As we only need accuracy for $x \in [0, 255]$, we can scale up the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{\alpha n}^{\alpha+1}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &=\frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} + \log{20}
  \end{split}
\end{align}
\section{Approximation for $x^r$}
To approximate $x^r$ for any $r \in \mathbb{R}$, we rewrite $x^r$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^r}} = e^{r\log{x}}.
\end{align*}
This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{r\log{x}} &= \sum_{n=0}^{\infty}{\frac{(r\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^r$.
